Incorporating Periodic Variability in Hidden Markov Models for Animal Movement

### 2016-08-03 bmc_template/manuscript.tex
tex problems

%% BioMed_Central_Tex_Template_v1.06
%%                                      %
%  bmc_article.tex            ver: 1.06 %
%                                       %

%%IMPORTANT: do not delete the first line of this template
%%It must be present to enable the BMC Submission system to
%%recognise this template!!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                     %%
%%  LaTeX template for BioMed Central  %%
%%     journal article submissions     %%
%%                                     %%
%%          <8 June 2012>              %%
%%                                     %%
%%                                     %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% For instructions on how to fill out this Tex template           %%
%% document please refer to Readme.html and the instructions for   %%
%% authors page on the biomed central website                      %%
%% http://www.biomedcentral.com/info/authors/                      %%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%% BioMed Central currently use the MikTex distribution of         %%
%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
%% http://www.miktex.org                                           %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% additional documentclass options:
%  [doublespacing]
%  [linenumbers]   - put the line numbers on margins

%%% loading packages, author definitions

%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
\documentclass{bmcart}

%%% Load packages
%\usepackage{amsthm,amsmath}
\usepackage{amsmath}
\usepackage{setspace}
\doublespacing
\usepackage{lineno}
\linenumbers
%\RequirePackage{natbib}
%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
%\RequirePackage{hyperref}
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                             %%
%%  If you wish to display your graphics for   %%
%%  your own use using includegraphic or       %%
%%  includegraphics, then comment out the      %%
%%  following two lines of code.               %%
%%  NB: These line *must* be included when     %%
%%  submitting to BMC.                         %%
%%  All figure files must be submitted as      %%
%%  separate graphics through the BMC          %%
%%  submission process, not included in the    %%
%%  submitted article.                         %%
%%                                             %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\includegraphic{}
\def\includegraphics{}

%%% Put your definitions there:
\startlocaldefs
\endlocaldefs

@@

@@

van de Kerk et al.\cite{kerk2015hidden} considered time-homogeneous models with 
a variety of candidate distributions %
--- log-Normal, Gamma, and Weibull distributions for step lengths
and von Mises and wrapped Cauchy distributions for the turning angle --- %
concluding on the basis of the Akaike information criterion (AIC) 
that Weibull step length and wrapped Cauchy turning angle distributions
were best.  
Since our analysis aims for simplicity and qualitative
conclusions rather than for picking the very best
predictive model, we focus on models that treat each step as
a univariate, log-Normally distributed observation, glossing
over both the differences in shape between
the three candidate step-length distributions and the effects
of considering multivariate (i.e., step length plus turning angle)
observations.  However, we do briefly compare log-Normal and Weibull
step-length distributions, with and without 
a von Mises-distributed turning angle included in the model (Figure~\ref{fig:BICred_plot}).
(Note that most movement analyses, including van de Kerk et al.
\cite{kerk2015hidden}, are only partially multivariate, 
treating step length and turning angle at a particular time
as multivariate observations for the purpose of HMM
analysis but neglecting possible correlations
between the two measures.)

@@

\section{Data accessibility}
Hourly step lengths and turning angles of male and female Florida pan- thers available at: http://ufdc.ufl.edu//IR00004241/00001.

@@

\section*{Competing interests}
  The authors declare that they have no competing interests.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                  The Bibliography                       %%
%%                                                         %%
%%  Bmc_mathpys.bst  will be used to                       %%
%%  create a .BBL file for submission.                     %%
%%  After submission of the .TEX file,                     %%
%%  you will be prompted to submit your .BBL file.         %%
%%                                                         %%
%%                                                         %%
%%  Note that the displayed Bibliography will not          %%
%%  necessarily be rendered by Latex exactly as specified  %%
%%  in the online Instructions for Authors.                %%
%%                                                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% if your bibliography is in bibtex format, use those commands:
\bibliographystyle{bmc-mathphys} % Style BST file (bmc-mathphys, vancouver, spbasic).
\bibliography{bmc_article}      % Bibliography file (usually '*.bib' )
% for author-year bibliography (bmc-mathphys or spbasic)
% a) write to bib file (bmc-mathphys only)
% @settings{label, options="nameyear"}
% b) uncomment next line
%\nocite{label}

>>>>

\documentclass{bmcart}

%%% Load packages
%\usepackage{amsthm,amsmath}
\usepackage{amsmath}
\usepackage{setspace}
\doublespacing
\usepackage{lineno}
\linenumbers
%\RequirePackage{natbib}
%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
%\RequirePackage{hyperref}
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\usepackage{graphicx}
% \def\includegraphic{}
% \def\includegraphics{}

\startlocaldefs
\endlocaldefs

@@

\titlepage
\

@@

van de Kerk et al.\cite{kerk2015hidden} considered time-homogeneous models with 
a variety of candidate distributions %
--- log-Normal, Gamma, and Weibull distributions for step lengths
and von Mises and wrapped Cauchy distributions for the turning angle --- %
concluding on the basis of the Akaike information criterion (AIC) 
that Weibull step length and wrapped Cauchy turning angle distributions
were best.  
Since our analysis aims for simplicity and qualitative
conclusions rather than for picking the very best
predictive model, we focus on models that treat each step as
a univariate, log-Normally distributed observation, glossing
over both the differences in shape between
the three candidate step-length distributions and the effects
of considering multivariate (i.e., step length plus turning angle)
observations.  However, we do briefly compare log-Normal and Weibull
step-length distributions, with and without 
a von Mises-distributed turning angle included in the model (Figure 2).
(Note that most movement analyses, including van de Kerk et al.
\cite{kerk2015hidden}, are only partially multivariate, 
treating step length and turning angle at a particular time
as multivariate observations for the purpose of HMM
analysis but neglecting possible correlations
between the two measures.)

@@

\section{Data accessibility}
Hourly step lengths and turning angles of male and female Florida panthers available at: http://ufdc.ufl.edu//IR00004241/00001.

@@

\section*{Competing interests}
  The authors declare that they have no competing interests.

% if your bibliography is in bibtex format, use those commands:
\bibliographystyle{bmc-mathphys} % Style BST file (bmc-mathphys, vancouver, spbasic).
\bibliography{panthers}      % Bibliography file (usually '*.bib' )
% for author-year bibliography (bmc-mathphys or spbasic)
% a) write to bib file (bmc-mathphys only)
% @settings{label, options="nameyear"}
% b) uncomment next line
%\nocite{label}
